---
title: "R Notebook"
output: html_notebook
---
packages
```{r}
library(haven)
library(ggplot2)
library(dplyr)
library(gt)
```
Import adae
```{r}
adae <- read_sas("https://github.com/elong0527/r4csr/raw/master/data-adam/adae.sas7bdat", 
    NULL)
adae


```
Import adsl
```{r}
adsl <- read_sas("https://github.com/elong0527/r4csr/raw/master/data-adam/adsl.sas7bdat", 
    NULL)
adsl
```
```{r}
ggplot(adae) +
  aes(x = AESEV, fill = TRTA) +
  geom_bar() +
  scale_fill_hue(direction = 1) +
  theme_minimal()
```















Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*. 

```{r}
plot(cars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
